
# Installation works great

```{r installation}
install.packages("devtools")
devtools::install_github("MonashBioinformaticsPlatform/varistran")
```

# Testing

Would be nice if in main description on the github page, the bottomly dataset
or one of the other test datasets was shown as setup as a test set.
I only discovered some test datasets by looking at the tests.

NBPSeq isn't mentioned as a dependency anywhere, but is required to run the
*vst_stability_plots.R* test.

Testing of the bottomly dataset in *vst_stability_plots.R* fails:

```
Bottomly

Error in validObject(.Object) :
  invalid class “DESeqDataSet” object: levels of factors in the design contain characters other than letters, numbers, '_' and '.'
```

I fixed this in a pull request and it seems to work fine. The rest of the
tests passed fine.

# Test on non-included dataset
Here we test on a dataset that wasn't included in the tests by generating
a fake example dataset and running it through.

```{r test-data}
library(DESeq2)
dds = makeExampleDESeqDataSet(n = 20000, m = 12, betaSD = 0, interceptMean = 4,
                              interceptSD = 2, dispMeanRel = function(x) 4/x + 0.1)
counts = counts(dds, normalized=FALSE)
condition = c(rep("A", 6), rep("B", 6))
design = model.matrix(~condition)
```

```{r varistran-vst}
y <- varistran::vst(counts, design=design)
print(varistran::vst_advice(y))
```
```{r stability-plot}
varistran::plot_stability(y, counts, design=design)
```

```{r plot-biplot}
varistran::plot_biplot(y)
```

Would be nice if the plot_heatmap function subset the variable genes so it
did not plot the whole thing by default.

```{r plot-heatmap}
varistran::plot_heatmap(y[1:20,])
```

# Further testing

```
R CMD check fails:

* using session charset: UTF-8
* checking for file ‘./DESCRIPTION’ ... ERROR
Required field missing or empty:
  ‘Author’
* DONE
```
